### 2023-05-07 paper.tex
Final few changes

Prefix masking, which corresponds to the rightmost masking pattern in Figure 
\ref{masking_patterns}, can be useful for example when translating. The prefix allows the
model to attend to the entire source language sentence and causal masking can be 
used only for the target language sentence prediction. For example when translating, given an input
such as \texttt{[BEGIN]The dog is red.[PAD][SEP]Koira on punainen.[END]}, prefix masking 
can allow the model to fully attend to the input up until \texttt{[SEP]}. Only after this
point does the model have to start generating an output of its own.
 \cite{raffel_exploring_2020}

@@

Hopefully this paper serves as a good introduction to the general landscape of 
transformers in language models and helps in understanding what is going on in
large language models.

>>>>

Prefix masking, which corresponds to the rightmost masking pattern in Figure 
\ref{masking_patterns}, can be useful for example when translating. The prefix allows the
model to attend to the entire source language sentence and causal masking can be 
used only for the target language sentence prediction. For example when translating, given an input
such as \texttt{[BEGIN]The dog is red.[SEP]Koira on punainen.[END]}, prefix masking 
can allow the model to fully attend to the input up until \texttt{[SEP]}. Only after this
point does the model have to start generating an output of its own.
 \cite{raffel_exploring_2020}

@@

Hopefully this paper serves as a good introduction to the general landscape of 
transformers in language models and helps in understanding what is going on 
under the hood in large language models.
